---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidymodels)
library(pins)
library(lubridate)
library(janitor)
library(doParallel)
library(xgboost)

options(scipen = 999)
```

```{r}
board <-
  board_folder(getwd())

train <- 
  board %>% 
  pin_read('train') %>% 
  mutate(day_of_week = as.factor(day_of_week))

valid <-
  board %>% 
  pin_read('valid') %>% 
  mutate(day_of_week = as.factor(day_of_week))

store <- 
  read.csv('store.csv') %>% 
  clean_names()
```


```{r}
set.seed(4)

train_sub <-
  train %>% 
  filter(store %in% c(1, 2)) %>% 
  left_join(store, by = c('store' = 'store'))


train_store <-
  train %>% 
  left_join(store, by = c('store' = 'store'))

```

# Feature Engineering Ideas
# Holidays (Christmas)
# days in promo2
# days since competition opened
# indicator for whether it's during a promo2 month
# month of year
# day of month
# use some store level data such as the
  : average sales for that store for that day -- but you need to be careful not to leak information with this.
  - think of other store level data as this will be the optimal approach
  
```{r}
names(train)
```
  


```{r}
train_store <-
  train_store %>% 
  mutate(
          week_of_year = week(date),
          month_of_year = month(date),
          month_abb = as.character(month(date, label = TRUE)),
          p2_start_date = make_date(year = promo2since_year, month = 1, day = 1) + weeks(promo2since_week),
          ind_promo2_month = ifelse(str_detect(promo_interval, month_abb) & date >= p2_start_date, 1, 0),
          months_in_promo2 = replace_na(interval(p2_start_date, date) / months(1), -1),
          competition_date = make_date(competition_open_since_year, competition_open_since_month, 1),
          months_competition = ifelse(competition_date <= date, round(interval(competition_date, date) / months(1), 0), NA)
    
  ) 
  

train_store
```




```{r}
xgb_rec <-
  recipe(
    sales ~
      day_of_week +
      # date + 
      # store +
      open +
      promo +
      state_holiday +
      school_holiday +
      store_type +
      assortment +
      competition_distance +
      promo2 +
      ind_promo2_month +
      months_in_promo2 +
      months_competition 
    , data = train_store
  ) %>% 
  step_dummy(state_holiday, one_hot = TRUE) %>% 
  step_dummy(store_type, one_hot = TRUE) %>% 
  step_dummy(assortment, one_hot = TRUE) %>% 
  step_mutate(
              day_of_week = as.numeric(as.character(day_of_week))
              ) 
  # update_role(store, new_role =  'id variable') %>%
  # update_role(date, new_role = 'id variable') 

# 
# exp_rec <-
#   recipe(
#     sales ~
#       day_of_week +
#       open +
#       promo 
#     , data = train_store
#   ) %>% 
#   step_mutate(day_of_week = as.numeric(as.character(day_of_week)))

juiced_rec <- juice(prep(xgb_rec))

juiced_rec



```
```{r}
set.seed(42)


sliding_period(train_store %>% arrange(date), date, period = 'month', lookback = Inf, assess_stop = 2, every = 4, complete = TRUE) %>% 
  mutate(train_data = map(splits, analysis),
         test_data = map(splits, assessment)) %>% 
  select(-splits) %>% 
  pivot_longer(-id) %>% 
  unnest(value) %>% 
  group_by(id, name) %>% 
  summarize(cnt = n(),
            min_date = min(date),
            max_date = max(date)) %>% 
  arrange(id, min_date)

```


```{r}
folds <- 
  sliding_period(train_store %>% arrange(date), date, period = 'month', lookback = Inf, assess_stop = 2, every = 4)

folds
```


```{r}


xgb_model <-
  boost_tree(
    trees = 500
  ) %>% 
  set_mode('regression') %>% 
  set_engine('xgboost')

xgb_wf <-
  workflow() %>% 
  add_recipe(xgb_rec) %>% 
  add_model(xgb_model)

keep_pred <- control_resamples(save_pred = TRUE, save_workflow = TRUE) 

xgb_res <-
  xgb_wf %>% 
  fit_resamples(resamples = folds,
                control = keep_pred,
                metrics = metric_set(mae))


```

```{r}
xgb_res %>% 
  select(id, splits) %>% 
    mutate(train = map(splits, analysis),
         test = map(splits, assessment)) %>% 
  unnest(train) %>% 
  group_by(id) %>% 
  summarize(cnt = n(),
            min_date = min(date),
            max_date = max(date))
```

```{r}
xgb_res %>% 
  select(id, .metrics) %>% 
  unnest(.metrics)
```
# Model Tuning
```{r}
set.seed(42)


xgb_model <-
  parsnip::boost_tree(
    trees = 500,
    min_n = tune(),
    tree_depth = tune(),
    learn_rate = tune(),
    loss_reduction = tune(),
    sample_size = tune(),
    mtry = tune()
  ) %>% 
  set_mode('regression') %>% 
  set_engine('xgboost')

xgb_wf <-
  workflow() %>% 
  add_model(xgb_model) %>% 
  add_recipe(xgb_rec)

xgb_params <-
  xgb_wf %>% 
  parameters() %>% 
  finalize(train_store)

cl <- makePSOCKcluster(detectCores()-1)
registerDoParallel(cl)



xgb_bs <-
  xgb_wf %>% 
  tune_bayes(
    resamples = folds,
    param_info = xgb_params,
    iter = 50,
    control = control_bayes(save_pred = TRUE, verbose = TRUE, no_improve = 25),
    metrics = metric_set(mae)
    
  )

stopCluster(cl)
  
```


```{r}
xgb_res %>% 
  collect_metrics()
```

```{r}
xgb_res %>% 
  collect_predictions() %>% 
  group_by(id) %>% 
  count()
```




